### 2017-11-30 exams/exam6/2.tex
Housekeeping.

\begin{solution}
\begin{verbatim}
// 5 pts for Note
class Note {
    String txt;
    List<Note> subnotes;

@@

// 4 pts for List
interface List<X> {}

@@

//> 4 pts for interface defintions

@@

//> 4 pts for accept methods
// in Note
    <R> R accept(NoteVisitor<R> v) {
        return v.visitNote(this.txt, this.subnotes);
    }

@@

\begin{solution}
\begin{verbatim}
//> 4 pts
// Nesting Depth with recursion
class NestDepthR implements NoteVisitor<Integer> {
    NestDepthR () {}
    public Integer visitNote(String txt, List<Note> subnotes) {
        return 1 + subnotes.accept(new NestDepthListR());
    }
}

//> 4 pts
class NestDepthListR implements ListVisitor<Note,Integer> {
    NestDepthListR () {}
    public Integer visitEmpty() {
        return 0;
    }
    public Integer visitCons(Note first, List<Note> rest) {
        return Math.max(first.accept(new NestDepthR()),
                        rest.accept(this));
    }
}
\end{verbatim}
\end{solution}

@@

@@

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage
\newpage
\end{enumerate}
\end{problem}

>>>>

\begin{solution}
\begin{verbatim}
// 3 pts for Note
class Note {
    String txt;
    List<Note> subnotes;

@@

// 2 pts for List
interface List<X> {}

@@

//> 3 pts for interface defintions

@@

//> 2 pts for accept methods
// in Note
    <R> R accept(NoteVisitor<R> v) {
        return v.visitNote(this.txt, this.subnotes);
    }

@@

\begin{solution}
\begin{verbatim}
//> 6 pts overall
// Nesting Depth with recursion
class NestDepthR implements NoteVisitor<Integer> {
    NestDepthR () {}
    public Integer visitNote(String txt, List<Note> subnotes) {
        return 1 + subnotes.accept(new NestDepthListR());
    }
}

class NestDepthListR implements ListVisitor<Note,Integer> {
    NestDepthListR () {}
    public Integer visitEmpty() {
        return 0;
    }
    public Integer visitCons(Note first, List<Note> rest) {
        return Math.max(first.accept(new NestDepthR()),
                        rest.accept(this));
    }
}
\end{verbatim}
\end{solution}

@@

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi

\begin{solution}
\begin{verbatim}
// 5 pts (including tests)
// in Note
    Boolean sameNote(Note s) {
        return this.txt.equals(s.txt)
            && this.subnotes.sameList(s.subnotes)
    }

// in List<X>
    Boolean sameList(List<X> l);
    Boolean sameEmpty(Empty<X> l);
    Boolean sameCons(Cons<X> l);

// in Empty<X>
    public Boolean sameList(List<X> l) { return l.sameEmpty(this); }
    public Boolean sameEmpty(Empty<X> l) { return true; }
    public Boolean sameCons(Cons<X> l) { return false; }

// in Cons<X>
    public Boolean sameList(List<X> l) { return l.sameCons(this); }
    public Boolean sameEmpty(Empty<X> l) { return false; }
    public Boolean sameCons(Cons<X> l) { 
        return this.first.equals(l.first)
            && this.rest.sameList(l.rest);
    }
\end{verbatim}
\end{solution}

@@

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi

\begin{solution}
\begin{verbatim}
// 4 pts (including tests)
// in Note
    int hashCode() { return this.txt.hashCode() + this.subnotes.hashCode(); }

// in Empty
    int hashCode() { return 17; }

// in Cons
    int hashCode() { return this.first.hashCode() + this.rest.hashCode(); }
\end{verbatim}
\end{solution}

\newpage
\newpage
\end{enumerate}
\end{problem}
